Modeling vertical-axis cross-flow turbine wakes

### 2015-08-12 paper.tex
Fix some labels

The $k$--$\omega$ SST and Spalart--Allmaras RANS model cases were verified for
convergence of the turbine mean power coefficient with respect to grid spacing
and timestep. The grid topology was fixed, but the number of cells per unit
length were scaled proportionally, maintaining the same background mesh cell
aspect ratio. Results for this parameter sweep are shown in
Figure~\ref{fig:spatial-grid-dep}, from which the final number of streamwise
grid points $N_x = 70$ was chosen. This corresponds to a total cell count of
approximately $5 \times 10^4$ for the 2-D cases and 16 million for the 3-D case.

@@

    \label{fig:spatial-grid-dep}
\end{figure}

Time step dependence was studied using the $N_x=70$ grid, the results from which
are shown in Figure~\ref{fig:timestep-dep}. It was seen that the
Spalart--Allmaras model converged well with decreasing time step, leading to a
final time step of 0.001 s. The results from the SST model show a local minimum,
at $\Delta t = 0.002$ s, which was the final time step chosen to run the
simulations.

@@

\begin{figure}[ht]
    \includegraphics[width=0.9\textwidth]{figures/mom_bar_graph}
    \caption{Weighted sum normalized momentum recovery terms for each CFD case
        and experiments\cite{Bachant2015-JoT} at $x/D=1$.} \label{fig:recovery}
\end{figure}

>>>>

The $k$--$\omega$ SST and Spalart--Allmaras RANS model cases were verified for
convergence of the turbine mean power coefficient with respect to grid spacing
and timestep. The grid topology was fixed, but the number of cells per unit
length were scaled proportionally, maintaining the same background mesh cell
aspect ratio. Results for this parameter sweep are shown in
Figure~\ref{fig:verification}, from which the final number of streamwise
grid points $N_x = 70$ was chosen. This corresponds to a total cell count of
approximately $5 \times 10^4$ for the 2-D cases and 16 million for the 3-D case.

@@

    \label{fig:verification}
\end{figure}

Time step dependence was studied using the $N_x=70$ grid, the results from which
are shown in Figure~\ref{fig:verification}. It was seen that the
Spalart--Allmaras model converged well with decreasing time step, leading to a
final time step of 0.001 s. The results from the SST model show a local minimum,
at $\Delta t = 0.002$ s, which was the final time step chosen to run the
simulations.

@@

    \includegraphics[width=0.9\textwidth]{figures/mom_bar_graph}

    \caption{Weighted sum normalized momentum recovery terms for each CFD case
        and experiments\cite{Bachant2015-JoT} at $x/D=1$.}

    \label{fig:recovery}
\end{figure}
